Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-16 paper/main.tex

\begin{figure}[h]
    \begin{tabular}{|r|r|r|r|r|}
        \hline
                       &\eval & \texttt{evalq} & \texttt{eval.parent} & \texttt{local} \\
       Static    sites  & \Staticeval & \Staticevalq & \Staticevalparent & \Staticlocal \\
       Exercised sites & \Triggeredeval & \Triggeredevalq & \Triggeredevalparent & \Triggeredlocal \\
        Invocations & \EvalsRnd & \EvalqsRnd & \EparentsRnd & \LocalsRnd \\
%        \% triggered & \Triggeredevalpercent & \Triggeredevalqpercent & \Triggeredevalparentpercent & \Triggeredlocalpercent \\
        \hline
    \end{tabular}
    \caption{Variants of \eval} \label{tab:variantseval}
\end{figure}

>>>>

\begin{figure}[h]
    \begin{tabular}{|r|r|r|r|r|}
        \hline
                       &\eval & \c{evalq} & \c{eval} & \c{local} \\[-2mm]
                       & & & \c{.parent} & \\
                       \hline
       Static    sites  & \Staticeval & \Staticevalq & \Staticevalparent & \Staticlocal \\
       Exercised sites & \Triggeredeval & \Triggeredevalq & \Triggeredevalparent & \Triggeredlocal \\
        Invocations & \EvalsRnd & \EvalqsRnd & \EparentsRnd & \LocalsRnd \\
%        \% triggered & \Triggeredevalpercent & \Triggeredevalqpercent & \Triggeredevalparentpercent & \Triggeredlocalpercent \\
        \hline
    \end{tabular}
    \caption{Variants of \eval} \label{tab:variantseval}
\end{figure}

Figure~\ref{tab:variantseval} shows, per variant of \eval, the number of static eval call sites in the corpus, the number of call sites among them that are exercised during tracing, and how many invocations to \eval it results to. Most call sites and invocations use the main version of \eval, not its variants.
